Title

### 2012-01-17 inc/laser/laser.tex
import oe paper to frequency double section

>>>>

Above a diode current of 25A (i.e., an output power of 2.3W), the laser exhibits spontaneous self-starting ML operation.
At a diode current around 29A, a maximum (or optimum) average mode-locked output power of $\sim$3.5W is obtained.
The 250fs pulses generated at this output power (Fig. 4(a)) correspond to a Kerr lens strength in the Yb:KGW crystal of $\sim4 \text{m}^{-1}$, which is readily accommodated by the resonator design (Fig. 3(b)).
For this $\sim$3.5W ML laser with a negative cavity GVD of $-5,200\text{fs}^2$ per round-trip, the full-width at
%page 8638
half maximum of the mode-locked spectrum centered at 1046nm is 4.7nm (Fig. 4(c)).
The laser is therefore generates pulses with a time-bandwidth product very close to the Fourier limit of 0.32 for a sech$^2$ pulse shape.
At output powers greater than 3.5W, a DC spectral component emerges at the short wavelength end of the ML spectrum (Fig. 4(d)) and there is a slow roll-over in the laser output power (Fig. 5).
This trend is expected for a Yb:KGW soliton ML laser; in this case, the soliton power limit being reached at about 29A, and the asymmetric spectral gain of Yb:KGW forcing excess CW laser power oscillation at wavelengths shorter than the peak of the ML spectrum.
Similar laser performance is observed with the insertion of an additional $-5,600\text{fs}^2$ of cavity GVD per round trip, which generates 347fs sech$^2$ pulses (Fig. 4(b)); that is, a DC spectral component appears on the short wavelength side of a narrower $\sim$3.5nm ML spectrum at output powers above 5W.

\subsection{Frequency doubling}
